\subsection{Product View}

Describe here the properties of the product View and provide diagrams showing the proposed structure for this view.

The Product View is...

The root nodes consist of the Rubin Observatory Operations Departments.




Directors Office
The Vera C. Rubin Observatory Director’s office is responsible for the overall management of the observatory and the survey as well as fulfilling the mission of the observatory and realizing its vision. The Director’s office includes a Directorate, Administrative Operations, Safety, Communications, and In-Kind Contributions teams.
Observatory Operations
The Chilean-based Rubin Observatory Operations Department is responsible for operating and maintaining the telescope, camera systems, and summit facilities in order to collect the raw imaging and housekeeping data needed by the Legacy Survey of Space and Time. The primary tasks include maintaining the operating facilities, conducting the night-time survey operations, real-time assessment of image quality and observing efficiency, performing the daily calibration, and collecting and analyzing engineering data.
Data Production
The role of the Rubin Observatory Data Production department is to accept data from the Observatory’s telescopes and ancillary systems; to process that data to generate science ready data products; to archive both raw data and derived data products; and, subject to approval from the Science Performance department and the Data Release Board, to make that data available to the scientific community. The Data Production department will develop, maintain and operate the networks, compute and storage hardware, and software that constitutes the Rubin Observatory Data Management System for the duration of the operational period.
System Performance
Rubin Observatory System Performance department is responsible for ensuring that the LSST as a whole is proceeding with the efficiency and fidelity needed to achieve its science requirements at the end of the 10-year survey. This includes the Wide-fast-Deep (WFD) survey and all Special Programs (deep drilling fields and mini-surveys). To meet this goal, the System Performance department will track and optimize the integrated performance of the entire system. This includes the performance of the observatory and the progress of the survey with respect to its science objectives, the ability of the community to access and analyze the data and publish results on the four LSST science pillars at an appropriate rate, the evaluation of strategies for improving the survey strategy, and the development of mitigation strategies together with other relevant departments to minimize the impact of changes in the system performance on the overall LSST science.
Education and Public Outreach
The mission of the Rubin Observatory Education and Public Outreach (EPO) program is to offer accessible and engaging online experiences that provide non-specialists access to, and context for, Rubin Observatory data so anyone can explore the Universe and be part of the discovery process. EPO serves as a website that highlights and contextualizes the scientific power of Rubin Observatory for non-specialists and hosts all online resources.