\documentclass[SE,lsstdraft, authoryear,toc]{lsstdoc}

% lsstdoc documentation: https://lsst-texmf.lsst.io/lsstdoc.html
\input{meta}

% Package imports go here.

% Local commands go here.

%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{Project-wide Documentation Proposal for Rubin Observatory Operations}

% Optional subtitle
\setDocSubtitle{(Report from the Rubin Observatory Documentation Working Group)}

\author{%
Chuck Claver (chair),
David Cabrera (co-Chair),
Rob McKercher (co-chair),
John Andrew,
Diane Hascall,
Patrick Ingraham,
Tony Johnson,
Kristen Metzger,
Austin Roberts,
Jonathan Sick,
Matthew Rumore.
}

\setDocRef{SITCOMTN-014}
\setDocUpstreamLocation{\url{https://github.com/lsst-sitcom/sitcomtn-014}}

\date{\vcsDate}

% Optional: name of the document's curator
\setDocCurator{Matthew Rumore}

\setDocAbstract{%
This technical note is a report to recommend a future state for Rubin Observatory Operations documentation by the Project-wide Documentation Working Group, as a final deliverable for the charge described in \url{LSE-489.lsst.io}.
This proposal presents a high-level documentation strategy for Rubin Observatory Operations with suggested methodologies to transition Construction Project documents and organizations for the technical documentation package needed to establish construction completeness and operational readiness.
The presented implementation plan for transitioning includes an estimated level of effort, resources, scheduling and risks if not implemented, as well as a method of sustained maintenance throughout Operations.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{0.0}{2021-06-26}{First draft of preliminary content.}{Chuck Claver}
  \addtohist{0.1}{2021-08-30}{Input to Documentation Portal.}{Jonathan Sick}
  \addtohist{0.2}{2021-09-14}{Preliminary content, Portal architecture and effort.}{Chuck Claver, Jonathan Sick}
  \addtohist{0.3}{2022-11-18}{Incorporate draft from Confluence pages and shared files as pre-draft.}{David Cabrera, Matthew Rumore}
  \addtohist{0.4}{2024-02-16}{Modifications.}{Matthew Rumore}
}


\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE
% You can also use the \input command to include several content files.

\input{Intro}

\input{DocumentViews}
\input{ProductView}
\input{StorageView}
\input{AccessView}
\input{TopicView}
%
\input{ImplementationPlan}
\input{PrimarySources}
\input{DocumentationPortal}
\input{DocuSharePath}
\input{PDMWorksPath}

% To remove in  refactoring (comment out)
 \input{ResourcesResponsibilities}
 \input{Schedule}

\input{TransitionWorkflow}

\input{RiskAssessment}

\newpage
\appendix

\input{AppendixExamples}

\newpage
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
%\printglossaries

\end{document}
